Reply to reviewers\\ LMCS \#\,6784 Manuscript: \\``Compositional equivalences based on Open pNets''

### 2021-10-19 2016-Weak-FH-Bisim/2021-09-letter2Reviewers.tex
one more pass in the train
small typo/style fixing.

\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more specifically for a process algebra with a choice operator and a $\tau$ action)

\item We improved related works with a positioning relatively to ``negative premisses'' and ``conditional transitions''.

@@

- The definition of pNets is cumbersome. I understand that this work extends prior work where the model has been motivated already, but I have my reservations on the utility of the formalisms.    I found the running example (although useful) to be hard to understand.  It would perhaps be useful to provide anecdotal evidence showing that comparable formalisms cannot handle certain features of the example (which would justify the complexity of the model used).
\begin{quote}
The definition of pNets is indeed not simple but as it is placed at a very generic and semantic leve,l we do not believe there are good alternatives in the literature. Process algebras for example do not feature the hierarchical and parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult. Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of existing parallel operators, and compositional reasoning on equivalence.

@@

2) Why not work directly in terms of Open Automata (and forget all about pNets)?  A prima facie, they appear to be of a comparable complexity to pNets (if not simpler).  There are few people who would be interested in using a framework that relies on the second rule in Def 9 as a modelling language...  
\begin{quote}
The reason for the coexistence of the two formalisms is that one is hierarchical and adapted to modelling, the other is flat and more based on logic, and adapted to semantic/equivalence reasoning.
We added one subsection in the introduction that presents the two formalisms and the reason why both exist.
\end{quote}

@@

l -6: why not use an asymmetric symbol instead of $\otimes$? 
%QUESTION: veut on vraiment changer de symbole?
A%NSWER:
\begin{quote}
$\otimes$ is a form of composition: we have changed for something similar to $\circ$, renamed it into $\odot$
\end{quote}

@@

P11 L1 What is X in the open transition $OT_x^{x\in X}$?
\begin{quote}
In the context of this article, we consider that an indexed set $OT_x^{x\in X}$ defines both an indexation set $X$ and a set of elements $OT_x$ for $x\in $. We additionally clarified this in the notation section. Additionally to the previous text that stated:
"$t_i^{i\in I}$ defines first $I$ the set over which the family is indexed, and then $a_i$ the elements of the family"
we added:
"Note that, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$."
\end{quote}

>>>>

\item We added an example illustrating the difference between our weak bisimulation and weak bisimulation for CCS (more generaly for a process algebra with a choice operator and a $\tau$ action)

\item We improved explanations wherever the reviewers indicated it was necessary (e.g.  semantics of pNets,  definition of bisimulation, definition of weak open transitions)

\item We improved related works with a positioning with respect to ``negative premisses'' and ``conditional transitions''.

@@

- The definition of pNets is cumbersome. I understand that this work extends prior work where the model has been motivated already, but I have my reservations on the utility of the formalisms.    I found the running example (although useful) to be hard to understand.  It would perhaps be useful to provide anecdotal evidence showing that comparable formalisms cannot handle certain features of the example (which would justify the complexity of the model used).
\begin{quote}
The definition of pNets is indeed not simple but as it is placed at a very generic and semantic level, we do not believe there are good alternatives in the literature. Process algebras for example do not feature the hierarchical and parametric aspects of pNets and defining equivalence checking tools on these frameworks is difficult. Of course the examples can be expressed in any concurrent Turing-complete model but none of the existing works feature the same results as ours on the modelling of classical parallel operators, and compositional reasoning on equivalence.

@@

2) Why not work directly in terms of Open Automata (and forget all about pNets)?  A prima facie, they appear to be of a comparable complexity to pNets (if not simpler).  There are few people who would be interested in using a framework that relies on the second rule in Def 9 as a modelling language...  
\begin{quote}
The reason for the coexistence of the two formalisms is that one is hierarchical and adapted to the modelling of high level languages, the other is flat and more based on logic, and adapted to semantic/equivalence reasoning.
We added one subsection in the introduction that presents the two formalisms and the reason why both exist.
\end{quote}

@@

l -6: why not use an asymmetric symbol instead of $\otimes$? 
%QUESTION: veut on vraiment changer de symbole?
A%NSWER:
\begin{quote}
$\otimes$ is a form of composition: we have changed for something similar to the functional composition symbol $\circ$, renamed it into $\odot$
\end{quote}

@@

P11 L1 What is X in the open transition $OT_x^{x\in X}$?
\begin{quote}
In the context of this article, we consider that an indexed set $OT_x^{x\in X}$ defines both an indexation set $X$ and a set of elements $OT_x$ for $x\in X$. We additionally clarified this in the notation section. Additionally to the previous text that stated:
"$t_i^{i\in I}$ defines first $I$ the set over which the family is indexed, and then $a_i$ the elements of the family"
we added:
"Note that, sentences of the form ``there exists $t_i^{i\in I}$'' means there exists $I$ and a function that maps each element of $I$ to a term $t_i$."
\end{quote}
